A significance test in forward stepwise regression

### 2014-03-14 paper/paper.tex
Paper: editing projection calculation

\newcommand{\grad}{\nabla}
\newcommand{\V}{\mathcal{V}}\endlocaldefs
\newcommand{\K}{\mathcal{K}}
\newcommand\tf{\widetilde{f}}
\newcommand{\pen}{\mathcal{P}}
\newcommand{\gstar}{g^*}

@@

We now describe how to calculate our p-value, following the discussion of
group lasso in \cite{tests:adaptive}. For the rest of this section let
$g = \gstar$ be the index of
the group attaining the maximum on line 3 of Algorithm~\ref{algo:fs}.
%\lambda = \norm{X_g^Ty}_2/w_g$ be the value of the maximum, and
%$r = \text{rank}(X_g)$ be the rank of the maximizing group.
For a vector $u \in \real^p$, let $u_h$ denote the coordinates
of $u$ corresponding to the columns of group $h$ in the design matrix $X$.
We can rearrange the columns of $X$ to group these adjacently, so that
\[
u^TX^T = \begin{pmatrix} u_1^T X_1^T & u_2^T X_2^T & \cdots & u_G^TX_G^T \end{pmatrix}
\]
One step of the calculation will be to find an orthonormal basis for the
linear space $V = \{ u \in \real^p : u_g^T X_g^T y = 0, u_h = 0
\text{ for all } h \neq g \}$ so that we can project orthogonally to
this space. If $X_g$ is a single column and $X_g^Ty \neq 0$, then the
space is trivial and the desired orthogonal projection is the identity.
Otherwise, if $X_g$ has $p_g > 1$ columns,

>>>>

\newcommand{\grad}{\nabla}
\newcommand{\V}{\mathcal{V}}\endlocaldefs
\newcommand{\K}{\mathcal{K}}
\newcommand\tf{\widetilde{f}}
\newcommand{\pen}{\mathcal{P}}
\newcommand{\vecsp}{\mathcal{L}}
\newcommand{\gstar}{g^*}

@@

We now describe how to calculate our p-value, following the discussion of
group lasso in \cite{tests:adaptive}. For the rest of this section let
$g = \gstar$ be the index of
the group attaining the maximum on line 3 of Algorithm~\ref{algo:fs}.
%\lambda = \norm{X_g^Ty}_2/w_g$ be the value of the maximum, and
%$r = \text{rank}(X_g)$ be the rank of the maximizing group.
For a vector $u \in \real^p$, let $u_h$ denote the coordinates
of $u$ corresponding to the columns of group $h$ in the design matrix $X$.
We can rearrange the columns of $X$ to group these adjacently, so that
\[
u^TX^T = \begin{pmatrix} u_1^T X_1^T & u_2^T X_2^T & \cdots & u_G^TX_G^T \end{pmatrix}
\]
One step of the calculation will be to find an orthonormal basis for the
linear space $\vecsp_g = \{ u \in \real^p : u_g^T X_g^T y = 0, u_h = 0
\text{ for all } h \neq g \}$ so that we can project orthogonally to
this space. If $X_g$ is a single column and $X_g^Ty \neq 0$ (which
should be the case since $g$ maximizes the absolute value of this
quantity), then the
space is trivial and the desired orthogonal projection is the identity.
Otherwise, if $X_g$ has $p_g > 1$ columns, the space $\vecsp_g$ will
generally
have dimension $r-1$ for $r = \text{rank}(X_g)$. This holds except in
degenerate cases such as $X_g = 0$ or $r \ll p_g$, but these cases are not
likely to occur since $\norm{X_g^T y}_2/w_g$ is supposed to be maximized.
We proceed by forming the $n \times p_g$ matrix
$X_g - X_g X_g^T y y^T X_g/\norm{X_g^Ty}_2^2$ and performing Gram-Schmidt
on the first $r-1$ columns. For precise theorems showing that this will
generally work, see \cite{outerp:indep}. Next we take the basis
computed by Gram-Schmidt and form an $p \times r-1$ matrix, which we
denote $V_g$, by appending 0's in the coordinates corresponding to all
groups $h \neq g$ and to $p_g - r + 1$ columns in group $g$. With this
we are ready to define the projection

\begin{equation}
  \begin{aligned}
    P_g &= \Sigma XV_g (V_g^T X^T \Sigma X V_g)^\dagger V_g^TX^T \\
  \end{aligned}
\end{equation}
